### 2019-10-30 README.Rmd
Import RSQLite and clarify the multi-db methods

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
taxadb:::td_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

```{r message = FALSE}
library(taxadb)
library(dplyr)
library(readr)
```

@@

```{r, message = FALSE}
bbs_species_list <- system.file("extdata/bbs.tsv", package="taxadb")
bbs <- read_tsv(bbs_species_list)
```

@@

See richer examples, including name cleaning and background on the schema in the vignettes:

- [Tutorial](https://cboettig.github.io/taxadb/articles/intro.html)
- [Schema](https://cboettig.github.io/taxadb/articles/articles/schema.html)

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
taxadb:::td_disconnect()
```

@@

```{r message = FALSE}
library(taxadb)
library(dplyr) # Used to illustrate how a typical workflow combines nicely with `dplyr`
```

@@

```{r, message = FALSE}
bbs_species_list <- system.file("extdata/bbs.tsv", package="taxadb")
bbs <- read.delim(bbs_species_list)
```

@@

- See richer examples the package [Tutorial](https://cboettig.github.io/taxadb/articles/intro.html).

- Learn about the underlying data sources and formats in [Data Sources](https://cboettig.github.io/taxadb/articles/articles/data-sources.html)

- Get better performance by selecting an alternative [database backend](https://cboettig.github.io/taxadb/articles/articles/backends.html) engines.
